Corona of an M7 fast rotator with a high latitude flare

### 2023-04-19 src/tex/ms.tex
[showyourwork] overleaf sync

@@

\begin{figure}[ht!]
    \script{FIGURE_lx_lbol.py}
    \begin{centering}
        \includegraphics[width=0.75\linewidth]{figures/lx_lbol.png}
        \caption{
         Rossby number versus $L_x/L_{bol}$.
        }
        \label{fig:lxlbol}
    \end{centering}
\end{figure}

>>>>

\begin{figure}[ht!]
    \script{FIGURE_data_resid.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/joint_onlyflare_data_resid.png}
        \caption{
         Flare only joint Double APEC spectrum fit.
        }
        \label{fig:spec_joint_onlyflare}
    \end{centering}
\end{figure}

\begin{figure}[ht!]
    \script{FIGURE_data_resid.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/joint_noflare_data_resid.png}
        \caption{
         Joint Double APEC spectrum fit with flare excluded.
        }
        \label{fig:spec_joint_noflare}
    \end{centering}
\end{figure}

\begin{figure}[ht!]
    \script{FIGURE_data_resid.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/joint_all_data_resid.png}
        \caption{
         Joint Double APEC spectrum fit.
        }
        \label{fig:spec_joint_all}
    \end{centering}
\end{figure}

@@

\begin{figure}[ht!]
    \script{FIGURE_lx_lbol.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/lx_lbol.png}
        \caption{
         Rossby number versus $L_x/L_{bol}$.
        }
        \label{fig:lxlbol}
    \end{centering}
\end{figure}
